\textbf{INSERT TITLE HERE}

### 2013-11-16 LaTeX/paper.tex
Added steps 5, 4, 3 and 2 in part 1; working in reverse order

\section{Assumptions and Justifications}
\begin{enumerate}
    \item
        The travel times given are calculated from an optimal route from the center of the first
        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item
        The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item
        The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item
        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
        (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{enumerate}

@@

\subsection{Part 1?}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.

\subsection{Ambulance Distributon Optimization}
Once the zone-to-zone coverages have been calculated, we must still decide where to place
the ambulances to maximize total coverage. Total coverage is defined as the sum of the coverages
of the individual zones, i.e. the number of people that can be reached by at least one ambulance
within eight minutes.

Since ambulance placements are assumed to be in the center of zones, putting two ambulances in the same
zone does not increase coverage. Therefore, ambulances should be placed in different zones to maximize
coverage.

Under the given conditions, we can easily find the optimal ambulance placement using a brute force
method: trying all $\binom{6}{3}$ choices of ambulance placements, and picking the one with the highest total coverage.
However, this solution is not scalable to larger cities, as the brute force method has time complexity
$O(n) = nk\binom{n}{k}$ where $n$ is the number of zones to cover, and $k$ is the number of ambulances to place, which
becomes intractable as $n$ and $k$ increase (since it has to check $\binom{n}{k}$ placements,
and calculating the total coverage of each placement requires $nk$ computations, summing the $k$ zone-zone
coverages for each of the $n$ ambulances). Quadrupling the size of the city
increases the computations required by a factor of 2 million (assuming the average zone size stays the same,
and the number of ambulances increases proportionally).

Therefore, a more scalable solution is needed. We discovered that a greedy heuristic also gives a good solution,
except with a much lower time complexity of $O(n) = n^2k$.

>>>>

\section{Assumptions and Justifications}
\begin{enumerate}
    \item The travel times given are calculated from an optimal route from the center of the first
        zone to the center of ths econd. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item
        Partial ambulance coverage of a zone will be treated as imcomplete even coverage ove the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage.
\end{enumerate}

@@

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}
    \item[$A(t), B(t)$] Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$Z_{AB}(t)$] Zone-to-zone coverage of  B from  A
    \item[$v$] required ambulance response time
    \item[$T_{AB}$] travel time from A to B, given
    \item[$T_{BA}$] travel time from B to A, given
    \item[$P_B$] total population of B
    \item[$F_B(s)$] the probability curve for differences in travel time within B
    \item[$T_{A^+}$] travel time inside of A traveling away from B
    \item[$T_{A^-}$] travel time inside of A traveling toward B
    \item[$T_{B^+}$] travel time inside of B traveling away from A
    \item[$T_{B^-}$] travel time inside of B traveling toward A
    \item[$a, b$] width of A and B respectively
    \item[$g$] width of the gap between A and B
\end{description}

%TODO: Graphical representation of origin and setup

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB}}_{T_{AB} - b} s F_B(s) ds$$

\subsection{Ambulance Distributor}
Once the zone-to-zone coverages have been
